---
title: "PSY 8712 Week 8 Project"
author: "Richard"
date: "2026-03-23"
output: html_document
---

# Reproducible Image and Online Resources

An image of this project as of *`r Sys.Date()`* can be accessed by clicking this [link](https://mybinder.org/v2/gh/rnlanders/datascience/HEAD). An interactive web app is available by [clicking this link](https://tntlab.shinyapps.io/shiny_week8/) instead.

# Script Settings and Resources

```{r echo=T, message=F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(GGally)
```

# Data Import and Cleaning
comment!
```{r}
week8_tbl <- read_csv("../data/week3.csv") %>%
    mutate(
      timeStart = ymd_hms(timeStart),
      condition = factor(condition, levels = c("A","B","C"), labels = c("Block A", "Block B", "Control")),
      gender = factor(gender, levels = c("M","F"), labels = c("Male","Female")),
      timeSpent = timeEnd - timeStart,
      q5 = 6 - q5,
      q1q6mean = rowMeans(across(q1:q6), na.rm=T),
      q8q10mean = rowMeans(across(q8:q10), na.rm=T)
    )
```

# Visualization
comment!
```{r echo=F, message=F, error=F}
select(week8_tbl, q1:q6) %>%
  ggpairs()
ggplot(week8_tbl,
       aes(x=q1q6mean, y=q8q10mean)) +
  geom_point() +
  geom_smooth(method="lm", color="purple")
```

# Analysis
`r paste("I observed a correlation of",
      str_remove(round(cor.test(week8_tbl$q1q6mean, week8_tbl$q8q10mean)$estimate,2), "^0"),
      "with a p-value of",
      round(cor.test(week8_tbl$q1q6mean, week8_tbl$q8q10mean)$p.value, 2)
)
`
```{r}
cor.test(week8_tbl$q1q6mean, week8_tbl$q8q10mean)
```
     
# Data Export  
comment!
```{r}
week8_tbl %>%
  mutate(timefilter = timeEnd > "2017-07-01") %>%
  select(q1q6mean, q8q10mean, timefilter, gender) %>%
  saveRDS("../shiny/shiny_week8/shiny.RDS")
```