---
title: "PSY 8712 Week 8 Project"
author: "Richard"
output: 
  html_document:
    df_print: paged
---

# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/rnlanders/datascience/HEAD?urlpath=rstudio). 

An interactive web app is available by [clicking this link instead](https://tntlab.shinyapps.io/shiny_week8/).

# Script Settings and Resources
```{r section2, message=F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# Data Import and Cleaning
Imported the week 3 dataset and reverse coded q5
```{r section3}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(q5 = 6-q5,
         timeStart = ymd_hms(timeStart),
         q1q6mean = rowMeans(across(q1:q6)),
         q8q10mean = rowMeans(across(q8:q10))
  ) %>%
  select(timeEnd, gender, q1:q6, q1q6mean, q8q10mean)
```

# Data Visualization
Subsetted on q1-q6 for display, then displayed calculated means
```{r section4, echo=F, message=F}
select(week8_tbl, q1:q6)
week8_tbl %>%
  ggplot(aes(x=q1q6mean, y=q8q10mean)) +
  geom_point() +
  geom_smooth(method="lm", color="purple")
```

# Analysis
calculated correlation between numbers
```{r section5}
cortest <- cor.test(week8_tbl$q1q6mean, week8_tbl$q8q10mean)
cortest
```
I observed a correlation of `r str_remove(formatC(cortest$estimate, format="f", digits=2), "^0")`. It was not statistically significant.

# Data Export
```{r section6}
week8_tbl %>%
  mutate(afterjuly1 = timeEnd > "2017-07-01 00:00:00") %>%
  select(gender, q1q6mean, q8q10mean, afterjuly1) %>%
  saveRDS("../shiny/shiny_week8/import.RDS")
```
